---
title: "MA615_GroupAssignment"
author: "Becky Yu , Mira Tang , Kecheng Liang , Chaoqun Yin"
date: "September 30, 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(readxl)
library(kableExtra)
```

We got the dataset from the [Suspicious Activities Report statistics](https://www.fincen.gov/reports/sar-stats) tool. After filtering specific industries (Insurance Company, Loan or Finance Company, Money Services BUsiness and Securities/Futures) and suspicious activities(Fraud), we got a dataset with 43454 observations of 8 variables. Looking into the data, we found that observations with "[Total]" entries were summarized data that should be seprated from raw data, so we removed those entires and ended with 23890 observations.

## Data Cleaning
```{r}
#Import data
Finance <- read.csv("SARStats.csv")
#View(Finance)
summary(Finance)

#Eliminate meaningless data
Finance <- filter(Finance, !(str_detect(string = Finance$State,pattern = "\\[Total\\]")))
Finance <- filter(Finance, !(str_detect(string = Finance$Industry,pattern = "\\[Total\\]")))
Finance <- filter(Finance, !(str_detect(string = Finance$Product,pattern = "\\[Total\\]")))
Finance <- filter(Finance, !(str_detect(string = Finance$Instrument,pattern = "\\[Total\\]")))
Finance <- filter(Finance, !(str_detect(string = Finance$Suspicious.Activity,pattern = "\\[Total\\]")))
Finance <- filter(Finance, !(str_detect(string = Finance$Regulator,pattern = "\\[Total\\]")))
Finance <- filter(Finance, !(str_detect(string = Finance$Year.Month,pattern = "\\[Total\\]")))

#rename the inappropriate column name
colnames(Finance)[1]<-"Year"

#Transform the type of data
Finance$Count <- as.numeric(Finance$Count)
```

##EDA

### State

Firstly, let us take a quick look at the total count of frauds reported in 2017 for each state:

```{r}
Finance %>% 
  group_by(Year,State) %>% 
  summarise(State_Total_Count = sum(as.numeric(Count)))-> State1

library(ggplot2)
library(maps)
#load us map data
all_states <- map_data("state")

#mutate the count data into map data
State2017<-State1[which(as.character(State1$Year)=='2017 '),]
State2017$State<-tolower(State2017$State)
s<-State2017$State
for (i in 1:length(s)){
  if (s[i] %in% unique(all_states$region)){
    all_states[which(all_states$region==s[i]),"count2017"]<-State2017$State_Total_Count[i]
  }
}

#plot all states with ggplot
ggplot(all_states)+
  geom_polygon(aes(x=long, y=lat, group = group,fill=count2017),colour="white" )

```

Next, here are the boxplots of total counts of all states per year:
```{r}
ggplot(State1, aes(x=Year, y=State_Total_Count))+
  geom_boxplot()+
  coord_flip()
```



#### Make a table
```{r}
#get a summarized dataframe with top five states for each year
Finance %>% 
  group_by(Year , State) %>% 
  summarise(Total_Count = sum(as.numeric(Count))) %>% 
  arrange(Year,desc(Total_Count)) %>% 
  slice(1:5) -> State2

#tidy the long table using string concating skills
table1<-aggregate(State~Year,data =State2,paste,collapse=",")
table2<-aggregate(Total_Count~Year,data =State2,paste,collapse=",")

#join the sub tables
table<-left_join(table1,table2,by="Year")
kable(table,caption = "Top five States each year", "html" ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

#### Make a plot
```{r}
ggplot(State2,aes(x = Year,y = Total_Count,fill = State))+
  geom_bar(stat = 'identity',position = 'stack') +
  labs(title = "Top Five States That Most Frauds Were Reported- Becky Yu")
```

The count of frauds reported increased largely through the last few years. Since the data of 2018 has not been complete yet, we may still predict a trend of growth. California and New York were typically among the top five States that most frauds were reported. Massachusetts ranked first in 2013 and 2014, but ended with fifth in 2015, 2016 and 2017.

### Industry
```{r}
Finance %>% group_by(Year,Industry)  %>%  
  summarize(Count = sum(Count)) %>%
  arrange(Year,desc(Count)) -> Finance.ind
```

#### Make a table
```{r}
kable(Finance.ind[,c(2,3)], caption = "Securities/Futures Suspicious Activity Reports by Industry" , "html" ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  group_rows("2012", 1, 3) %>%
  group_rows("2013", 4, 6) %>%
  group_rows("2014", 7, 10) %>%
  group_rows("2015", 11, 14) %>%
  group_rows("2016", 15, 18) %>%
  group_rows("2017", 19, 22) %>%
  group_rows("2018", 23, 26)
```

#### Make a plot
```{r}
ggplot(Finance.ind,aes(x = Year , Count ,fill = Industry)) +
  geom_bar(stat = "identity",position = "fill",width = 0.8) +
  coord_polar(theta = "x") +
  labs(title = "Mira Tang")
```

We can know from the plot that MSB is the most frequent industry reported securities/futures suspicious activity in each year. Although insurance company's suspicious activities happend a lot in 2012, it decreased by year.

### Suspicious Activities
```{r}
#Select some useful columns from the database
suspicion <- select(Finance, Year, Suspicious.Activity, Count)

# Change the column's name
colnames(suspicion)[1] <- "Year"
suspicion %>%
  group_by(Year, Suspicious.Activity) %>%
  summarize(Count = sum(Count)) %>%
  arrange(Year, desc(Count)) %>%
  slice(1:5) -> sus.table
```

#### Make a table
```{r}
kable(sus.table, caption = "Top 5 Reported Susicious Activities by Years") %>%
  kable_styling(bootstrap_options = c("striped") )
```

#### Make a plot
```{r}
ggplot(suspicion, aes(x = Year, y = Count, fill = Suspicious.Activity)) +
  geom_col(position = "stack") +
  labs(title = "Kecheng Liang")
```

The graph shows that we should pay more attetion on wire, credit/debit card, and check.

### Regulator
```{r}
#Seclect the columns for analysis
regulator <- select(Finance, Year, Regulator, Count)

#Change the name of the years
colnames(regulator)[1]<-"Year"
```

#### Make a table
```{r}
regulator %>% group_by(Year,Regulator) %>% 
  summarize(Count=sum(Count)) %>% 
  arrange(Year,desc(Count)) %>%
  slice(1:3)-> sus.table

kable(sus.table, caption = "Top 3 Regulators against Criminal") %>%
  kable_styling(bootstrap_options = c("striped") )
```

#### Make a plot
```{r}
ggplot(regulator , aes(x = Year,y = Count,fill = Regulator)) + 
  geom_col(position = "stack") + 
  labs(title = "Chaoqun Yin")
```

From the plot, the most financial criminal cases are handled by IRS and SEC.